Algomusicology, ????, Profit

### 2016-07-23 paper.tex
Incorporate detailed feedback from reviewer 3.

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. That's roughly the size all music ever recorded,
described in less than a half a tweet.~\footnote{Based on the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
restricted to 140 characters.}

>>>>

Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
takes very little space at all. That is roughly five times the the size of the entire iTunes library,
described in less than a half a tweet.~\footnote{Based on the the iTunes library featuring approximately 50 million songs
of approximately 4 megabytes each. Tweets are restricted to 140 characters.}
